Figures for conference paper

### 2019-04-26 conference figures.Rmd
shape of data boxes as cylinder

```{r}
grViz("digraph flowchart {

@@

      subgraph cluster_input_data {
      label = 'Data';
      style = filled;
		  color = lightgrey;
		  node [style = filled, color = black, fillcolor = white];
      CD [label = 'Course Data']
      SD [label = 'Student Data']
      }

@@

      # Invisible node
      node [shape = circle, width = .01, height = .01, label = '']
      x1 x2

@@

      SD -> AP;
      {SD, TM} -> TE;
      {TR, KW} -> AI;
      {ID, SD} -> TR;
      {PM, CS, TR} -> GP;
      GP -> WAR;
		  {TM, PM, WAR} -> PRE;

@@

@@

```{r}
df_logLike_catalogue %>%
  ggplot(aes(x = n_topic, y = LogLikelihood)) +
  geom_vline(xintercept = 80, col = "red", alpha = 0.5, linetype = "dashed") +
  geom_line() +

>>>>

```{r}
grViz("digraph flowchart{

@@

      subgraph cluster_input_data {
      label = 'Data';
      style = filled;
		  color = lightgrey;
		  node [style = filled, color = black, fillcolor = white, shape = cylinder];
      CD [label = 'Course Data']
      SD [label = 'Student Data']
      }

@@

      # Invisible node
      node [shape = circle, width = .01, height = .01, label = '']
      x1 x2 x3

@@

      SD -> AP;
      {SD, TM} -> TE;
      {TR, KW} -> AI;
      {ID, SD} -> TR;
      {PM, CS, TR} -> GP;
      GP -> WAR;
		  WAR -> PRE;

@@

      edge[label = '']
      {TM, PM} -> x3 [arrowhead = none]
      edge[label = 'KL distance', decorate = TRUE]
      x3 -> PRE;

@@

```{r}
max_LL <- df_logLike_catalogue$n_topic[which.max(df_logLike_catalogue$LogLikelihood)]

df_logLike_catalogue %>%
  ggplot(aes(x = n_topic, y = LogLikelihood)) +
  geom_vline(xintercept = max_LL, col = "red", alpha = 0.5, linetype = "dashed", size = 1) +
  geom_line(linetype = "dashed") +
  geom_point() +
